A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-13 04_Severity_MetaAnalysis.Rmd
update percent severity as a function of the median

```{r}
PM_dat_D$yi_percent <- log(((PM_dat_D$PM_final_severity - 1)/8) * 100 +1)
PM_dat_D$vi_percent <- ((PM_dat_D$vi)/8)* 100
hist(PM_dat_D$yi_percent)
summary(PM_dat_D$yi_percent)
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = yi_percent,
   V = vi_percent,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvPer)
```
Model does not converge we will proceed with the square transformed severity

@@

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,6:11),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",

>>>>

```{r}
PM_dat_D$yi_percent <- ((PM_dat_D$PM_final_severity)/median(PM_dat_D$PM_final_severity) * 100)
PM_dat_D$vi_percent <- PM_dat_D$vi/median(PM_dat_D$PM_final_severity)
hist(PM_dat_D$yi_percent)
summary(PM_dat_D$yi_percent)
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = yi_percent,
   V = vi,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

summary(PMsev_mvPer)
# Intecep <- coef(PMsev_mvPer)[1]
# ((coef(PMsev_mvPer)[2:6]+ Intecep)/100)* median(PM_dat_D$PM_final_severity) - (Intecep/100*median(PM_dat_D$PM_final_severity))
```
Model does not converge we will proceed with the square transformed severity

@@

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were back transformed using a square-root from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,6:11),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
